Presentation Title

### 2017-05-29 thesis/chapters/ch1-intro.tex
Write trustchain intro

We begin the detailed discussion by formulating the model \autoref{sec:model}. 
Next, we analyse the correctness, security and performance of our design in \autoref{sec:analysis},
this is where we present our theorems.
Implementation and experimental results are discussed in \autoref{sec:implementation}.
Finally, we compare our system with other state-of-the-art blockchain systems and conclude in Sections \ref{sec:related} and \ref{sec:conclusion} respectively.

>>>>

We begin the detailed discussion by formulating the model \Cref{sec:model}. 
Next, we analyse the correctness, security and performance of our design in \Cref{sec:analysis},
this is where we present our theorems.
Implementation and experimental results are discussed in \Cref{sec:implementation}.
Finally, we compare our system with other state-of-the-art blockchain systems and conclude in Sections \ref{sec:related} and \ref{sec:conclusion} respectively.
